A meta-analysis of mental rotation ability in the first years of life

### 2022-04-19 code/analysis.Rmd
Prepare comparison of gender grouping strategies

# Show number of experiments per gender grouping strategy
table(dat$gender_split)

# Extract mixed/split experiments only
dat_mixed <- filter(dat, gender_split %in% c("mixed", "mixed_only"))
dat_split <- filter(dat, gender_split %in% c("split", "split_only"))

# Extract both strategies combined (but excluding any redundant experiments)
dat_both <- filter(
  dat, gender_split %in% c("mixed", "mixed_only", "split_only")
)

# Correlations between dependent samples
summary(dat$ri)
```

@@

```{r, compute_meta, echo=TRUE}
# Compute standard error of Cohen's d based on assumed correlation
# This will need a sensitivity analysis
r_assumed <- 0.5
dat_both %>%
  mutate(
    ni = sample_size,
    sei = sqrt(((2 * (1 - r_assumed)) / ni) + (yi^2 / (2 * ni))),
    age_months = age_mean / 30.417
  ) %>%
  select(article, group, age_months, female_percent, ni, yi, sei) %>%
  # Compute sampling variance from standard errors
  escalc(yi = yi, sei = sei, ni = ni, data = .) %>%
  tibble() -> dat_r

# Create vector of experiment IDs for plotting
experiment_ids <- with(dat_r, paste(article, group, sep = ", "))

# # Two-level model
# res <- rma(
#   yi, vi,
#   data = dat_r,
#   slab = experiment_ids
# )
# print(res)
# forest(res)

# Three-level model
res_mv <- rma.mv(
  yi, vi,
  random = ~ 1 | article / group,
  data = dat_r,
  slab = experiment_ids
)
print(res_mv)
forest(res_mv)

@@

# # Profile likelihodd plots
# profile(res_mv, tau2 = 1)
# profile(res_mv, rho = 1)

# Meta-regression with age
res_age <- rma.mv(
  yi, vi,
  mods = ~age_months,
  random = ~ group | article,
  data = dat_r,
  slab = experiment_ids
)
print(res_age)
forest(res_age)

# Meta-regression with gender
res_gender <- rma.mv(
  yi, vi,
  mods = ~female_percent,
  random = ~ group | article,
  data = dat_r,
  slab = experiment_ids
)
print(res_gender)
forest(res_gender)

# Meta-regression with age, gender, and their interaction
res_full <- rma.mv(
  yi, vi,
  mods = ~ age_months * female_percent,
  random = ~ group | article,
  data = dat_r,
  slab = experiment_ids
)
print(res_full)
forest(res_full)
```

@@

# Run Bayesian multilevel model
res_brm <- brm(
  yi | se(sei) ~ 1 + (1 | article / group),
  data = dat_r,
  prior = prior_c,
  cores = 4,
  chains = 4,
  iter = 2000,
  sample_prior = TRUE,
  save_pars = save_pars(all = TRUE)
)
summary(res_brm)

>>>>

# Get empirical estimate of the correlation between dependent samples
summary(dat$ri)

# Compute standard error of Cohen's d based on assumed correlation
# This will need a sensitivity analysis
r_assumed <- 0.5
dat %>%
  mutate(
    ni = sample_size,
    vi = ((2 * (1 - r_assumed)) / ni) + (yi^2 / (2 * ni)),
    sei = sqrt(vi),
    age_months = age_mean / 30.417,
    age_months_c = age_months - mean(age_months, na.rm = TRUE)
  ) %>%
  filter(!is.na(yi)) %>%
  select(
    article, group, gender_split, age_months_c, female_percent, yi, ri, vi, sei
  ) -> dat_r

# Show number of experiments per gender grouping strategy
table(dat_r$gender_split)

# Extract mixed/split experiments only
dat_mixed <- filter(dat_r, gender_split %in% c("mixed", "mixed_only"))
dat_split <- filter(dat_r, gender_split %in% c("split", "split_only"))

# Combine both strategies, preferring mixed experiments
dat_both_mixed <- filter(
  dat_r, gender_split %in% c("mixed", "mixed_only", "split_only")
)

# Combine both strategies, preferring mixed experiments
dat_both_split <- filter(
  dat_r, gender_split %in% c("split", "mixed_only", "split_only")
)
```

@@

```{r, compute_meta, echo=TRUE}
# # Two-level model
# res <- rma(
#   yi, vi,
#   data = dat_r,
#   slab = experiment_ids
# )
# print(res)
# forest(res)

# Three-level model
res_mv <- rma.mv(
  yi, vi,
  random = ~ 1 | article / group,
  data = dat_both_mixed,
  slab = paste(article, group, sep = ", ")
)
print(res_mv)
# forest(res_mv)

@@

# # Profile likelihodd plots for checking that REML has converged
# profile(res_mv)

# Meta-regression with age
res_age <- rma.mv(
  yi, vi,
  mods = ~age_months_c,
  random = ~ 1 | article / group,
  data = dat_both_mixed,
  slab = paste(article, group, sep = ", ")
)
print(res_age)
# forest(res_age)

# Meta-regression with gender
res_gender <- rma.mv(
  yi, vi,
  mods = ~female_percent,
  random = ~ 1 | article / group,
  data = dat_both_mixed,
  slab = paste(article, group, sep = ", ")
)
print(res_gender)
# forest(res_gender)

# Meta-regression with age, gender, and their interaction
res_full <- rma.mv(
  yi, vi,
  mods = ~ age_months_c * female_percent,
  random = ~ 1 | article / group,
  data = dat_both_mixed,
  slab = paste(article, group, sep = ", ")
)
print(res_full)
# forest(res_full)
```

@@

# Run prior predictive simulation
res_prior <- brm(
  yi | se(sei) ~ 1 + (1 | article / group),
  data = dat_both_mixed,
  prior = prior_c,
  cores = 4,
  chains = 4,
  iter = 2000,
  sample_prior = TRUE,
  save_pars = save_pars(all = TRUE)
)
summary(res_brm)
